The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-05-12 albatros_paper.tex
work on solar section, add some more detail

\subsection{Solar power system}
\attention{Nivek, Tankiso, Eamon?} \\
The power system of the ALBATROS-EGG uses generators to charge the batteries manually every once in a number of days. From the observation that has been made, the batteries take $\approx$ 2 days to discharge to a point where the system shuts down. Because of the weather conditions in Marion Island, an individual can sometimes be unable to go to the site to charge the batteries, which means that if the weather does not allow, the system can be shut down for a long period. Thus, a solar power system solution was introduced to the ALBATROS so that the system can continously run without having to be recharged manually and often.\\

The ALBATROS system is powered using \SI{24}{\volt} power which is stored and provided by two series-connected \SI{12}{\volt} deep-cycle lead-acid storage batteries. This power comes from the solar panel array consisting of nine flexible solar panels, each with a standard test condition capacity of \SI{110}{\watt}. The solar panel type is SunPower SPE-E-Flex-110. The panels are grouped in three parallel connected strings of three panels. Each group of three is mounted on its own structure. The panels include diodes to bypass shaded or defective cells, and also to prevent backwards current flow in the event an entire string of three panels is not illuminated while the others are producing power. \\

The Victron BlueSolar MPPT 50$\vert$35 charge controller outputs a data packet every second, to an Arduino based data logger, which controls a switch that determines when the rest of the system runs. It also converts the solar panel voltage to \SI{24}{\volt} to control the battery charging. The observed parameters are then stored to the raspberry pi.

>>>>

\subsection{Solar power system}
\attention{Nivek, Tankiso, Eamon?} \\
Although the first-deployed two-element pathfinder is located at a reasonable walking distance from the main base and uses a generator to periodically recharge batteries, the bulk of the antenna stations that will comprise the full array will be located at points farther removed from the main base, and will require a fully autonomous energy source. So in deploying the autonomous station pathfinder, we developed a solar charging system to power the station.

The autonomous station is powered by two series-connected 12V deep-cycle lead-acid batteries, charged by an array of nine  SunPower SPE-E-Flex-110 solar panels. These panels each have a standard test capacity of 110W. Although only $\sim$50W is required to run the station (and the station may typically be powered on only over night) the $\sim$1kW charging capacity is sized to allow the charge level to recover quickly on a short sunny day in winter if it runs down due to several consecutive overcast days.

The nine solar panels are distributed between three custom-designed structures built from aluminum extrusion, with rigid metalized plastic panels backing the semi-flexible solar cells. The structures are oriented due north, and are designed to incline the solar panels at a relatively steep angle so as to maximize peformance under winter conditions, when sunlight hours will be at their minimum. The solar panel mounts have been designed to withstand frequent gale-force winds on Marion. While the mounting structures themselves appear to be strong enough, the greatest challenge in deployment has been to find an adequate anchoring technique in the volcanic ground.

Each group of three panels is wired in series, and the three series strings are connected in parallel to a Victron BlueSolar MPPT 50$\vert$35 charge controller, which optimizes power transfer from the solar array when charging is required, and also monitors charge level, reducing charge current when the battery bank is fully charged.

A power logging and control system runs on an Arduino, which logs information received from the Victron charge controller to an SD card, and switches power on and off to the receiver chassis. Logged power data will be used to refine powers system requirements for future autonomous station deployments. The on/off control is necessary to prevent battery system  damage from overly deep discharge. The system can also be configured to conserve battery power by running on a schedule between particular hours, typically overnight, since visibility may be better and ionosopheric noise levels lower.

The power logging and control system, along with the Victron charge controller and an EMI filter, are housed together in an aluminum box. The EMI filter reduces conducted emissions on the photovoltaic side of the solar charge controller, which could radiate from the solar array and connecting wires. (It may be noted however, that signals collected at night, which are expected to be more valuable, are not at risk of solar charge controller EMI contamination.)

\iffalse
The ALBATROS system is powered using \SI{24}{\volt} power which is stored and provided by two series-connected \SI{12}{\volt} deep-cycle lead-acid storage batteries. This power comes from the solar panel array consisting of nine flexible solar panels, each with a standard test condition capacity of \SI{110}{\watt}. The solar panel type is SunPower SPE-E-Flex-110. The panels are grouped in three parallel connected strings of three panels. Each group of three is mounted on its own structure. The panels include diodes to bypass shaded or defective cells, and also to prevent backwards current flow in the event an entire string of three panels is not illuminated while the others are producing power. \\

The Victron BlueSolar MPPT 50$\vert$35 charge controller outputs a data packet every second, to an Arduino based data logger, which controls a switch that determines when the rest of the system runs. It also converts the solar panel voltage to \SI{24}{\volt} to control the battery charging. The observed parameters are then stored to the raspberry pi.
\fi
